---
title       : Diamond Pricer
subtitle    : Effectively pricing diamonds using linear modelling
author      : Simon Frost
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
--- .class #id

## Intro

Diamond Pricer is a quick and easy application to price your diamonds based on their cut, colour and clarity built on Shiny and R technology using statistical modelling. We use the diamonds dataset from ggplot2.

```{r data, echo=FALSE}
library(ggplot2)
data("diamonds")
head(diamonds)
```

--- 

## Getting the right price is very important

```{r echo=F, dev.args = list(bg = 'transparent')}
hist(diamonds$price, main="Histogram of Diamond Prices", xlab="Diamond Prices($)")
```

---

## A quick plot

Carat, clarity and cut are good predictors, and should be easy to fit a linear model.

```{r echo=F, dev.args = list(bg = 'transparent')}
ggplot(data = diamonds, aes(x = carat, y = price, color = clarity, shape = cut)) + geom_point()
```

---

## The model

We fit the following model, taking into account relationship between carat and price:

```
lm((log(price)) ~ I(carat^(1/3)) + carat + cut + clarity, data = diamonds)
```

---

## The Result

[https://spli.shinyapps.io/DiamondPricer/]

Please click and give it a go!

